Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
figure alignment

\begin{subfigure}{.2\textwidth}
{\small
\begin{verbatim}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y;
  *(&y-2) = 0;
  return 5;
}
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
{\small
\begin{verbatim}
1 main: add $1,%sp      ; allocate frame
2       mov $42,-1(%sp) ; initialize local
3       call f
4       add -1(%sp),%ra ; set return value
5       sub $1,%sp      ; deallocate frame
6       ret

10 f:   add $1,%sp      ; allocate frame
11      mov $0,-3(%sp)  ; violation!
12      mov $5, %ra     ; set return value
13      sub $1,%sp      ; deallocate frame
14      ret
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}{.25\textwidth}
\begin{center}
\begin{tabular}{l l}
{\tt 2} &
\memoryaddrs{8em}
\memory{3}{\unsealc}[Unseal]
~$\cdots$
\vspace{.5em}
\\
{\tt 3} &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
{\tt 11} &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[Seal(0)]%
\memory{1}{\retptrc}[RetPtr]%
\memory{1}{\unsealc}[Unseal]
~$\cdots$
\MemoryLabel{-15em}{0.75em}{42}
\vspace{.5em}
\\
{\tt 12} &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}

\vspace{\abovedisplayskip}
\end{subfigure}
\caption{An integrity violation\bcp{Can we align the C-like snippets with
    the corresponding assembly?\apt{Maybe, but it would require adding blank lines
      at places in both the C and asssembly, making them harder to read
  and eating more space.}\bcp{I'm just talking about removing the space
  above "main" in the left column and moving f down a bit.}}
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
  colored backgrounds under the different parts}\fi}
\label{fig:int1}
\end{figure}

This section introduces the intuition behind the properties through a series
of examples. Existing stack safety enforcement work mostly refers directly to examples
of bad behavior that it prevents; we will argue that: \bcp{Not sure this
  enumeration is useful.}

@@

\begin{figure}
\begin{subfigure}{.2\textwidth}
{\small
\begin{verbatim}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y,z;
  y = 5;
  z = *(&y-2);
  return y+z;
}
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
{\small
\begin{verbatim}
1 main: add $1,%sp      ; allocate frame
2       mov $42,-1(%sp) ; initialize local
3       call f
4       add -1(%sp),%ra ; set return value
5       sub $1,%sp      ; deallocate frame
6       ret

>>>>

\begin{subfigure}[t]{.2\textwidth}
{\small
\begin{verbatim}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y;
  *(&y-2) = 0;
  return 5;
}
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}[t]{.5\textwidth}
{\small
\begin{verbatim}
1 main: add $1,%sp      ; allocate frame
2       mov $42,-1(%sp) ; initialize local
3       call f
4       add -1(%sp),%ra ; set return value
5       sub $1,%sp      ; deallocate frame
6       ret

10 f:   add $1,%sp      ; allocate frame
11      mov $0,-3(%sp)  ; violation!
12      mov $5, %ra     ; set return value
13      sub $1,%sp      ; deallocate frame
14      ret
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}[t]{.25\textwidth}
\begin{center}
\begin{tabular}{l l}
{\tt 2} &
\memoryaddrs{8em}
\memory{3}{\unsealc}[Unseal]
~$\cdots$
\vspace{.5em}
\\
{\tt 3} &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
{\tt 11} &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[Seal(0)]%
\memory{1}{\retptrc}[RetPtr]%
\memory{1}{\unsealc}[Unseal]
~$\cdots$
\MemoryLabel{-15em}{0.75em}{42}
\vspace{.5em}
\\
{\tt 12} &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}

\vspace{\abovedisplayskip}
\end{subfigure}
\caption{An integrity violation
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
  colored backgrounds under the different parts}\fi}
\label{fig:int1}
\end{figure}

This section introduces the intuition behind the properties through a series
of examples. Existing stack safety enforcement work mostly refers directly to examples
of bad behavior that it prevents; we will argue that: \bcp{Not sure this
  enumeration is useful.}\apt{+1}

@@

\begin{figure}
\begin{subfigure}[t]{.2\textwidth}
{\small
\begin{verbatim}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y,z;
  y = 5;
  z = *(&y-2);
  return y+z;
}
\end{verbatim}
}
\end{subfigure}
\begin{subfigure}[t]{.5\textwidth}
{\small
\begin{verbatim}
1 main: add $1,%sp      ; allocate frame
2       mov $42,-1(%sp) ; initialize local
3       call f
4       add -1(%sp),%ra ; set return value
5       sub $1,%sp      ; deallocate frame
6       ret
